---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CoronaShiny

<!-- badges: start -->
[![R build status](https://github.com/etc5523-2020/r-package-assessment-vvuu0009/workflows/R-CMD-check/badge.svg)](https://github.com/etc5523-2020/r-package-assessment-vvuu0009/actions)
<!-- badges: end -->

The goal of CoronaShiny is to ...

## Installation

<!-- You can install the released version of CoronaShiny from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("CoronaShiny") -->
<!-- ``` -->

The development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2020/r-package-assessment-vvuu0009")
```

This package contains the shiny application and functions exploring the current state of coronavirus as at 31 July 2020.

The main functions in this package includes:

- **launch_app**: This function runs the Coronavirus Shiny Application exploring the state of Coronavirus as at July 31 2020  
- **cumplot**: This function produces a line graph of coronavirus cases for a selected case type and continent with date on the x-axis and daily cases for the selected `Type` and `Continent` on the y-axis.
- **selectInput01**: This function changes the selectInput function of the Shiny app based on the desired input 

This package also contains the following data sets:

- **corona_cont**: This data set shows the daily coronavirus cases by each continent by case type
- **coronavirus_july20**: This data set shows the cumulative coronavirus cases as at 31 July 2020 for each country 

## Example

Below displays a sample of both data sets:

```{r corona_cont}
library(CoronaShiny)
library(tibble)
corona_cont
```

```{r coronavirus_july20}
coronavirus_july20
```

Below displays an example cumplot for confirmed cases in Asia

```{r}
cumplot("confirmed", "Asia")
```

