---
title: "Current State of Coronavirus Around the World"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Current State of Coronavirus Around the World}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 6.5
)
```

```{r setup}
library(CoronaShiny)
```

This package contains the shiny application and functions exploring the current state of coronavirus as at 31 July 2020.

The main functions in this package includes:

- **launch_app**: This function runs the Coronavirus Shiny Application exploring the state of Coronavirus as at July 31 2020  
- **cumplot**: This function produces a line graph of coronavirus cases for a selected case type and continent with date on the x-axis and daily cases for the selected `Type` and `Continent` on the y-axis.
- **selectInput01**: This function changes the selectInput function of the Shiny app based on the desired input 

This package also contains the following data sets:

- **corona_cont**: This data set shows the daily coronavirus cases by each continent by case type
- **coronavirus_july20**: This data set shows the cumulative coronavirus cases as at 31 July 2020 for each country 

## Launching Application

The applicaiton can be launched by using the following line of code:

```{r launch, eval=FALSE}
launch_app()
```


## Example

Below displays a sample of both data sets:

```{r corona_cont}
library(tibble)
corona_cont
```

```{r coronavirus_july20}
coronavirus_july20
```

Below displays an example cumplot for confirmed cases in Asia

```{r cumplot}
cumplot("confirmed", "Asia")
```


Below displays an example use of the selectInput01 function to select `Type` as the select input variable from the `coroan_cont` dataset.

```{r selectInput01 , eval=FALSE}
selectInput01("type", corona_cont$type)
```

